---
title: "lab_report_knapsack"
author: "Zahra Jalilpour and Arslan Shirazi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this package we create three different functions ,brute force, dynamic programming and greedy heuristic. We examine our functions by random values of weight and values. v is between 0 to 10000 and w is the range of 1 to 4000



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsack)
set.seed(42)
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)

```
## Brute force algorithm
The first function is related to Brute force algorithm. In this algorithm the complexity is O(2^n), for n items.  
knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500)
The highest value for the first eighth items without exceeding the max weight of 3500 is about 17277value-units and items 4,5,7 are used.
By system.time({
+     knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500)
we calculate the time that algorithm take to solve the problem.
