---
title: "vignette_lab6"
author: "Zahra, Arslan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_lab6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(error = TRUE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsack)
```


```{r analysis, include=TRUE}
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000))
```
#  knapsack problem 


The package will contain three different functions for solving what is called the knapsack problem.
The knapsack problem is a discrete optimization problem where we have a knapsack that can take a
limited weight W and we want to ll this knapsack with a number of items i = 1; :::; n, each with a
weight wi and a value vi. The goal is to nd the knapsack with the largest value of the elements added
to the knapsack.

We use three different function to solve this problem:
<p>
**1. brute_force_knapsack**

**2. knapsack_dynamic**

**3. greedy_knapsack**

## Brute force function

The only solution that is guaranteed to give a correct answer in all situations for the knapsack problem
is using brute-force search, i.e. going through all possible alternatives and return the maximum value
found. This approach is of complexity $O(2^n)$ since all possible combinations $2^n$ needs to be evaluated.
for time running, by microbenchmark library we will see the mean time as below. The mean run time is 334ms.

```{r runCode, echo=TRUE}
set.seed(42)
n <- 16
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
brute_force_knapsack(knapsack_objects[1:16,],3500)
system.time(brute_force_knapsack(knapsack_objects[1:16,],3500))
microbenchmark(brute_force_knapsack(knapsack_objects[1:16,],3500))
```

```
$value
[1] 40581

$elements
[1]  3  4  7 13 15


   user  system elapsed 
   0.36    0.00    0.36 
Unit: milliseconds
                                                 expr      min       lq     mean   median       uq     max
 brute_force_knapsack(knapsack_objects[1:16, ], 3500) 316.5239 323.9394 334.5155 326.1359 329.9637 688.664
 neval
   100
```   
## Dynamic Programming
<p> The second algorithm we use for knapsack problem is dynamic.The running time of the dynamic programming solution is $O(Wn)$. It is a way to improve the running time. As we see the running time is decreased compared to Brute Force function. The mean of run time is 44 ms.
```{r}
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 500
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
knapsack_dynamic(knapsack_objects[1:12,],3500)
system.time(knapsack_dynamic(knapsack_objects,3500))
microbenchmark(knapsack_dynamic(knapsack_objects[1:12,],3500))
```
```
$value
[1] 21612

$elements
[1] 6 7 9
 user  system elapsed 
   1.79    0.01    1.80 
Unit: milliseconds
                                             expr      min       lq     mean   median       uq      max
 knapsack_dynamic(knapsack_objects[1:12, ], 3500) 41.25938 42.62357 44.82965 44.70053 45.09591 101.3004
 neval
   100
```
##  greedy_knapsack()
<p> A last approach is to use the a heuristic or approximation for the problem. This algorithm will not
give an exact result (but it can be shown that it will return at least 50% of the true maximum value),
but it will reduce the computational complexity considerably (actually to $O(n log n)$ due to the sorting.
```{r}
set.seed(42)
n <- 10000
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
greedy_knapsack(knapsack_objects[1:12,],3500)
system.time(greedy_knapsack(knapsack_objects[1:12,],3500))
microbenchmark(greedy_knapsack(knapsack_objects[1:12,],3500))
```


```
   user  system elapsed 
      0       0       0 

Unit: milliseconds
                                            expr      min       lq     mean   median       uq      max
 greedy_knapsack(knapsack_objects[1:12, ], 3500) 1.608195 1.688759 1.755914 1.716212 1.754954 4.343255
 neval
   100
part of the algorithm)
```