---
title: "vignette_lab6"
author: "Zahra, Arslan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_lab6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsack)
```


```{r}
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000))
```
# ** knapsack problem **
The package will contain three different functions for solving what is called the knapsack problem.
The knapsack problem is a discrete optimization problem where we have a knapsack that can take a
limited weight W and we want to ll this knapsack with a number of items i = 1; :::; n, each with a
weight wi and a value vi. The goal is to nd the knapsack with the largest value of the elements added
to the knapsack.

We use three different function to solve this problem:
**1. brute_force_knapsack**

**2. knapsack_dynamic**

**3. greedy_knapsack**

## Brute force search

The only solution that is guaranteed to give a correct answer in all situations for the knapsack problem
is using brute-force search, i.e. going through all possible alternatives and return the maximum value
found. This approach is of complexity $O(2^n)$ since all possible combinations $2^n$ needs to be evaluated.

```{r}
set.seed(42)
n <- 16
knapsack_objects <- data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
brute_force_knapsack(knapsack_objects[1:16,],3500)
system.time(brute_force_knapsack(knapsack_objects[1:16,],3500))
```

$value
[1] 40581

$elements
[1]  3  4  7 13 15

> system.time(brute_force_knapsack(knapsack_objects[1:16,],3500))
   user  system elapsed 
   0.36    0.00    0.36 